Synthesizing Quotient Lenses

### 2018-03-14 papers/QuotientLenses/main.tex
Edited abstract
New figure

Indeed this idea is what motivates our definition of {\em QRE lenses}.
Intuitively, our QRE lenses are bijective lenses with ``canonizers at the edges,''
just like Boomerang's quotient lenses. 
Figure~\ref{fig:attheedges} depicts the architecture of QRE lenses.
\begin{figure}[t]
\centering
\includegraphics[width=0.7\textwidth]{canonizers-outside}
\caption{QRE Lens with ``Canonizers at the Edges''}
\label{fig:attheedges}
\end{figure}
Every QRE lens $q_1$ has a type $q_1: Q_1 \Leftrightarrow Q_2$ where $Q_1$ and $Q_2$
are QREs. In the {\em get} direction, a QRE lens $q_1: Q_1 \Leftrightarrow Q_2$ uses the
source QRE $Q_1$ to compute a canonical representative for the data modulo the
equivalence relation defined by $Q_1$ and then applies the $\get$ function of a
bijective string lens $\ell_1$ to this representative. In the {\em put} direction, $q_1$
operates similarly, but using the QRE $Q_2$ and the $\lput$ function of
$\ell_1$.

>>>>

Indeed this idea is what motivates our definition of {\em QRE lenses}.
Intuitively, our QRE lenses are bijective lenses with ``canonizers at the edges,''
just like Boomerang's quotient lenses. 
Figure~\ref{fig:attheedges} depicts the architecture of QRE lenses.
\begin{figure}[t]
\centering
\includegraphics[width=0.7\textwidth]{QREs}
\caption{QRE lens from source $P$ to target $Q$.  $P$
  and $Q$ are QREs, each consisting of a ``whole'' set ($W(P)$ and $W(Q)$)
  and a ``kernel'' part ($K(P)$ and $K(Q)$)
  Between the two kernels is a plain bijective lens.  The {\emph get}
  function of the whole lens takes an argument from $W(P)$, applies the
  canonizer for $P$ to obtain a canonical representative in $K(P)$, then
  applies the {\em get} of the plain lens, yielding an element of $K(Q)$,
  which is a subset of $W(Q)$.  The {\em put} function does the reverse,
  mapping from $W(Q)$ to $K(P)$ (hence $W(P)$.\BCP{Both the figure and the
    caption are new---what do you think??  Too detailed?  Unreadable?}}
\label{fig:attheedges}
\end{figure}
Every QRE lens $q_1$ has a type $q_1: Q_1 \Leftrightarrow Q_2$ where $Q_1$ and $Q_2$
are QREs. In the {\em get} direction, a QRE lens $q_1: Q_1 \Leftrightarrow Q_2$ uses the
source QRE $Q_1$ to compute a canonical representative for the data modulo the
equivalence relation defined by $Q_1$ and then applies the $\get$ function of a
bijective string lens $\ell_1$ to this representative. In the {\em put} direction, $q_1$
operates similarly, but using the QRE $Q_2$ and the $\lput$ function of
$\ell_1$.
